---
title: "Hot Keyboard Time: Data Cleaning with Dplyr"
output: 
  learnr::tutorial:
    language: "en"
    progressive: true
    allow_skip: true
    toc: true
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
chooseCRANmirror(graphics = FALSE, ind = 1)
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      out.width="100%")

if (!require(pacman)) install.packages("pacman")

p_load(
  lubridate,
  here,
  rio,
  tidyverse
)

# Load the wvs dataset
wvs <- import("https://drhuyue.site:10002/Adrian/data/wvs7.rda")
```

## Exercise 1: arrange()

Use the `arrange()` function to sort the data.

```{r arrange-exercise, exercise=TRUE}
# Sort by age in ascending order
wvs %>% 
  arrange(___)

# Sort by age in descending order
wvs %>% 
  arrange(___(___))

# Sort by age and income level
wvs %>% 
  arrange(___, ___)
```

```{r arrange-exercise-solution}
# Sort by age in ascending order
wvs %>% 
  arrange(age)

# Sort by age in descending order
wvs %>% 
  arrange(desc(age))

# Sort by age and income level
wvs %>% 
  arrange(age, incomeLevel)
```

## Exercise 2: select()

Use the `select()` function to choose specific columns.

```{r select-exercise, exercise=TRUE}
# Select country, age, and education columns
wvs %>% 
  select(___, ___, ___)

# Select all columns except country
wvs %>% 
  select(___)

# Select all columns containing "confidence_"
wvs %>% 
  select(___(___))

# Move the country column to the front
wvs %>% 
  select(___, ___)
```

```{r select-exercise-solution}
# Select country, age, and education columns
wvs %>% 
  select(country, age, education)

# Select all columns except country
wvs %>% 
  select(-country)

# Select all columns containing "confidence_"
wvs %>% 
  select(contains("confidence_"))

# Move the country column to the front
wvs %>% 
  select(country, everything())
```

## Exercise 3: filter()

Use the `filter()` function to select specific rows.

```{r filter-exercise, exercise=TRUE}
# Select rows where age is greater than 30
wvs %>% 
  filter(___ > ___)

# Select female respondents
wvs %>% 
  filter(___ == ___)

# Select respondents who are over 30 and female
wvs %>% 
  filter(___ > ___ & ___ == ___)

# Select countries where the maximum age is over 80
wvs %>% 
  group_by(___) %>% 
  filter(___(___) > ___)

# Select countries with a sample size of 36
wvs %>% 
  group_by(___) %>% 
  filter(___ == ___)
```

```{r filter-exercise-solution}
# Select rows where age is greater than 30
wvs %>% 
  filter(age > 30)

# Select female respondents
wvs %>% 
  filter(female == TRUE)

# Select respondents who are over 30 and female
wvs %>% 
  filter(age > 30 & female == TRUE)

# Select countries where the maximum age is over 80
wvs %>% 
  group_by(country) %>% 
  filter(max(age) > 80)

# Select countries with a sample size of 36
wvs %>% 
  group_by(country) %>% 
  filter(n() == 36)
```

## Exercise 4: mutate()

Use the `mutate()` function to create new variables.

```{r mutate-exercise, exercise=TRUE}
# Create an age group variable
wvs %>% 
  mutate(age_group = case_when(
    ___ < 30 ~ "Young",
    ___ < 60 ~ "Middle-aged",
    ___ >= 60 ~ "Old"
  ))

# Add a new constant column
wvs %>% 
  mutate(___ = ___)

# Create multiple new columns
wvs %>% 
  mutate(wave = ___,
         Year = ___)

# Create an age-centered variable by gender
wvs %>% 
  group_by(___) %>% 
  mutate(mean_age_centered_by_gender = ___ - ___(___))
```

```{r mutate-exercise-solution}
# Create an age group variable
wvs %>% 
  mutate(age_group = case_when(
    age < 30 ~ "Young",
    age < 60 ~ "Middle-aged",
    age >= 60 ~ "Old"
  ))

# Add a new constant column
wvs %>% 
  mutate(wave = 7)

# Create multiple new columns
wvs %>% 
  mutate(wave = 6,
         Year = 2014)

# Create an age-centered variable by gender
wvs %>% 
  group_by(country) %>% 
  mutate(mean_age_centered_by_gender = age - mean(age))
```

## Exercise 5: summarize()

Use the `summarize()` function to aggregate data.

```{r summarize-exercise, exercise=TRUE}
# Calculate the mean age
wvs %>% 
  summarize(mean_age = ___(___))

# Calculate multiple statistics
wvs %>%
  summarize(mean_age = ___(___),
            median_age = ___(___))

# Group by country and calculate statistics
wvs %>% 
  group_by(___) %>% 
  summarize(mean_age = ___(___),
            median_age = ___(___),
            count = ___())
```

```{r summarize-exercise-solution}
# Calculate the mean age
wvs %>% 
  summarize(mean_age = mean(age, na.rm = TRUE))

# Calculate multiple statistics
wvs %>%
  summarize(mean_age = mean(age, na.rm = TRUE),
            median_age = median(age, na.rm = TRUE))

# Group by country and calculate statistics
wvs %>% 
  group_by(country) %>% 
  summarize(mean_age = mean(age, na.rm = TRUE),
            median_age = median(age, na.rm = TRUE),
            count = n())
```

## Exercise 6: Combining Functions

Try to combine the above functions to solve complex problems.

```{r combine-exercise, exercise=TRUE}
wvs %>%
  filter(___) %>% 
  select(___, ___, ___) %>% 
  arrange(___) %>% 
  mutate(___) %>% 
  group_by(___) %>% 
  summarize(mean_age = ___,
            median_age = ___,
            count = ___)
```

```{r combine-exercise-solution}
wvs %>%
  filter(age > 30) %>% 
  select(country, age, education) %>% 
  arrange(age) %>% 
  mutate(wave = 7) %>% 
  group_by(country) %>% 
  summarize(mean_age = mean(age, na.rm = TRUE),
            median_age = median(age, na.rm = TRUE),
            count = n())
```

Please try to complete the above exercises and explain each step of the operation.
