---
title: "Hot Keyboard Time: Data Visualization with ggplot2"
output: 
  learnr::tutorial:
    language: "en"
    progressive: true
    allow_skip: true
    toc: true
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
chooseCRANmirror(graphics = FALSE, ind = 1)
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      out.width="100%")

if (!require(pacman)) install.packages("pacman")

p_load(
  lubridate,
  here,
  rio,
  tidyverse
)

# Load the wvs dataset
wvs <- import("https://drhuyue.site:10002/Adrian/data/wvs7.rda")
```

## Exercise 1: Scatter Plot

Use ggplot2 to create a scatter plot of education level versus income level.

```{r scatter-exercise, exercise=TRUE}
# Create a basic scatter plot
ggplot(data = wvs, aes(x = ___, y = ___)) +
  geom_point()

# Add color based on religious belief
ggplot(data = wvs, aes(x = incomeLevel, y = education, color = ___)) +
  geom_point()

# Add a smoothing line
ggplot(data = wvs, aes(x = incomeLevel, y = education, color = religious)) +
  geom_point() +
  geom_smooth(method = ___, se = ___)

# Customize the plot
ggplot(data = wvs, aes(x = incomeLevel, y = education, color = religious)) +
  geom_point(alpha = ___) +
  geom_smooth(method = "lm", se = TRUE) +
  labs(title = "___",
       subtitle = "___",
       x = "___", 
       y = "___") +
  theme_minimal()
```

```{r scatter-exercise-solution}
# Create a basic scatter plot
ggplot(data = wvs, aes(x = incomeLevel, y = education)) +
  geom_point()

# Add color based on religious belief
ggplot(data = wvs, aes(x = incomeLevel, y = education, color = religious)) +
  geom_point()

# Add a smoothing line
ggplot(data = wvs, aes(x = incomeLevel, y = education, color = religious)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE)

# Customize the plot
ggplot(data = wvs, aes(x = incomeLevel, y = education, color = religious)) +
  geom_point(alpha = 0.3) +
  geom_smooth(method = "lm", se = TRUE) +
  labs(title = "Education Level vs Income Level",
       subtitle = "Grouped by Religious Belief",
       x = "Income Level", 
       y = "Education Level") +
  theme_minimal()
```

## Exercise 2: Bar Plot

Create a bar plot showing the proportion of education levels by income level.

```{r bar-exercise, exercise=TRUE}
# Prepare the data
prop_data <- wvs %>%
  group_by(___, ___) %>%
  summarise(count = n()) %>%
  mutate(proportion = ___)

# Create a basic bar plot
ggplot(data = prop_data, aes(x = ___, y = ___, fill = ___)) +
  geom_bar(stat = "identity", position = "dodge")

# Customize the plot
ggplot(data = prop_data, aes(x = incomeLevel, y = proportion, fill = factor(education))) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "___",
       x = "___",
       y = "___",
       fill = "___") +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = ___),
    legend.position = "___",
    axis.text.x = element_text(angle = ___, hjust = 1)
  ) +
  scale_fill_brewer(palette = "___")
```

```{r bar-exercise-solution}
# Prepare the data
prop_data <- wvs %>%
  group_by(incomeLevel, education) %>%
  summarise(count = n()) %>%
  mutate(proportion = count / sum(count))

# Create a basic bar plot
ggplot(data = prop_data, aes(x = incomeLevel, y = proportion, fill = factor(education))) +
  geom_bar(stat = "identity", position = "dodge")

# Customize the plot
ggplot(data = prop_data, aes(x = incomeLevel, y = proportion, fill = factor(education))) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Proportion of Education Levels by Income Level",
       x = "Income Level",
       y = "Proportion",
       fill = "Education Level") +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom",
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  scale_fill_brewer(palette = "Set3")
```

## Exercise 3: Line Plot

Create a line plot showing the average education level for each income level, grouped by gender.

```{r line-exercise, exercise=TRUE}
# Prepare the data
avg_education <- wvs %>%
  group_by(___, ___) %>%
  summarise(avg_education = ___)

# Create a basic line plot
ggplot(data = avg_education, aes(x = ___, y = ___, color = ___)) +
  geom_line()

# Add points and customize the plot
ggplot(data = avg_education, aes(x = incomeLevel, y = avg_education, color = female)) +
  geom_line() +
  geom_point() +
  labs(title = "___",
       x = "___",
       y = "___",
       color = "___") +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = ___),
    legend.position = "___"
  ) +
  scale_color_manual(values = c("___", "___"), labels = c("___", "___"))
```

```{r line-exercise-solution}
# Prepare the data
avg_education <- wvs %>%
  group_by(incomeLevel, female) %>%
  summarise(avg_education = mean(education, na.rm = TRUE))

# Create a basic line plot
ggplot(data = avg_education, aes(x = incomeLevel, y = avg_education, color = female)) +
  geom_line()

# Add points and customize the plot
ggplot(data = avg_education, aes(x = incomeLevel, y = avg_education, color = female)) +
  geom_line() +
  geom_point() +
  labs(title = "Average Education Level by Income Level and Gender",
       x = "Income Level",
       y = "Average Education Level",
       color = "Gender") +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom"
  ) +
  scale_color_manual(values = c("blue", "red"), labels = c("Male", "Female"))
```

## Exercise 4: Combining Plot Types

Create a plot that combines a scatter plot with a box plot to show the distribution of education levels for each income level.

```{r combined-exercise, exercise=TRUE}
# Create a combined plot
ggplot(data = wvs, aes(x = ___, y = ___)) +
  geom_boxplot(alpha = ___) +
  geom_jitter(alpha = ___, width = ___)

# Customize the combined plot
ggplot(data = wvs, aes(x = factor(incomeLevel), y = education)) +
  geom_boxplot(alpha = 0.5) +
  geom_jitter(alpha = 0.2, width = 0.2) +
  labs(title = "___",
       x = "___",
       y = "___") +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = ___),
    axis.text.x = element_text(angle = ___, hjust = 1)
  )
```

```{r combined-exercise-solution}
# Create a combined plot
ggplot(data = wvs, aes(x = factor(incomeLevel), y = education)) +
  geom_boxplot(alpha = 0.5) +
  geom_jitter(alpha = 0.2, width = 0.2)

# Customize the combined plot
ggplot(data = wvs, aes(x = factor(incomeLevel), y = education)) +
  geom_boxplot(alpha = 0.5) +
  geom_jitter(alpha = 0.2, width = 0.2) +
  labs(title = "Distribution of Education Levels by Income Level",
       x = "Income Level",
       y = "Education Level") +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
```

Please try to complete the above exercises and explain each step of the visualization process.
